Assessing environmental and predator impacts on Antarctic Krill (*Euphausia superba*) population dynamics from an integrated length-to-age assessment model perspective

### 2025-05-16 MS2_Krill.Rmd
close work until..

Understanding the population dynamics of Antarctic krill (*Euphausia superba*) is critical for achieving sustainable and ecosystem management objectives in the Western Antarctic Peninsula (WAP). In this study, we implement an integrated length-to-age model that not only allows the incorporation of diverse data sources related to krill population dynamics, but also enables the evaluation of ecosystem influences—specifically environmental variability and predation pressure—on recruitment, biomass, and stock status. We explored multiple scenarios that accounted for ecosystem influences on krill population dynamics, yielding results that align with the expected behavior of a stock assessment framework tailored to this type of species. Performance analyses reveal systematic differences across scenarios, highlighting increased bias in fishing mortality (F) and spawning stock biomass (SSB) in models that exclude ecosystem variables. Conversely, the inclusion of environmental and predator data results in lower estimates of recruitment, total biomass, and spawning biomass, offering a more precautionary—and arguably more realistic—representation of krill population dynamics. Despite ongoing challenges in incorporating ecosystem variables into integrated model like this, we argue that these factors should be embedded directly into the state equations that govern population dynamics, rather than addressed through post hoc analyses. Overlooking these drivers may result in less accurate conclusions, hence limiting the effectiveness of management recommendations. Integrated modeling approaches that draw on extensive biological, fishery, and environmental datasets provide a valuable foundation for developing management strategies aligned with CCAMLR’s objectives for conservation and sustainable use.

@@

The residuals are visualized by year and length bin, allowing an assessment of model fit over time and across the size structure of the population (Figure \@ref(fig:pearson)). In scenario s1.1 (Without Ecosystem Variables), substantial lack of fit is evident across multiple years and length classes, particularly in the late 1990s and early 2000s. Positive Pearson residuals indicate that the model tends to underestimate frequencies of certain length bins, especially among smaller and mid-sized individuals, suggesting poor representation of recruitment and growth dynamics in the absence of environmental and predator effects. s1.2 (With Predator) shows some improvement in model fit, with slightly more balanced residuals. However, there are still consistent deviations in the mid-size ranges across multiple years, indicating that predation alone does not fully explain observed variability in length composition. In s1.3 (With Environment), there is a noticeable reduction in residual magnitude across several years and size classes, implying that incorporating environmental covariates helps align the model more closely with observed size distributions. This is particularly apparent in the early 2000s, where the residuals are closer to zero across most bins. Finally, s1.4 (With Predator and Ecosystem) shows the most consistent reduction in Pearson residuals across time and size structure. The residual patterns also indicate potentially concerning model misfits, particularly among adult individuals in several survey fleets operating in the Bransfield Strait, as well as among the largest size classes in the predator fleet, which likely represents penguin consumption data. The residuals exhibit consistent over- or under-estimation in specific length bins over multiple years, suggesting that the current model structure may not fully capture key processes affecting the abundance or selectivity of adult individuals. In the case of surveys in Bransfield, this could reflect spatial mismatches between predicted and observed size distributions or biases in survey selectivity for larger size classes. This spatial heterogeneity aligns with previous findings identifying this area as a core juvenile krill habitat [@Mardones2025; @Veytia2021, Vetia et al., 2019, REF, REF]. Similarly, the residuals associated with the predator fleet suggest that the model may inadequately represent size-selective predation or the temporal dynamics of predator consumption. These patterns warrant further investigation into the assumptions underlying length selectivity and mortality, particularly for the adult component of the population, as well as potential ecosystem-driven variability not currently integrated in the model.

@@

```{r pearson, eval=TRUE, fig.cap= "Pearson residuals of predicted versus observed length-frequency distributions of Antarctic krill across four modeling scenarios (s1.1 to s1.4), each incorporating increasing levels of ecosystem complexity. Residuals are shown by fleet, survey, and predator source, allowing visual assessment of model fit across time and sampling components (Red = positive, Black = negative"}
knitr::include_graphics('Figs/Pearson.png')
```

@@

Retrospective analyses were conducted to evaluate model performance across four scenarios incorporating different levels of ecosystem complexity (Figure \@ref(fig:rhoplot)). The retrospective pattern for fishing mortality (F) showed a marked increase in bias in scenario s1.4, which included both predator and environmental components, particularly in the terminal year. In this scenario, the combined rho value exceeded 3.5, indicating a strong retrospective pattern. Scenarios s1.2 (predator only) and s1.3 (environment only) also showed elevated rho values relative to s1.1 (baseline model without ecosystem variables), although the magnitude was lower than in s1.4. In contrast, the retrospective pattern for spawning stock biomass (SSB) was consistently negative across all scenarios and years. However, models that included environmental components—s1.3 and s1.4—tended to show larger negative biases in SSB, with scenario s1.4 again exhibiting the most pronounced pattern. The combined rho values for SSB in s1.3 and s1.4 were close to –0.5 and –0.6, respectively, whereas s1.1 showed a comparatively milder retrospective trend.

@@

Log-likelihood profiles were examined for each model scenario (s1.1 to s1.4) to assess how different components contributed to the overall model fit. Across all scenarios, the TOTAL log-likelihood is primarily influenced by the Survey, Length composition, and Recruitment components, with minor contributions from parameter priors. The reference model (s1.1) displays the highest overall likelihood value, particularly due to a stronger fit to the Length composition and Survey data. However, this comes with an elevated penalty in the parm priors categories, suggesting potential overfitting or parameter instability. In contrast, the ecosystem-informed scenarios—s1.2 (with predator data), s1.3 (with environmental data), and s1.4 (with both)—show slightly lower total likelihoods. These models present more balanced likelihood contributions across data components and generally lower penalties for parameter priors and deviations, indicating a more stable parameterization despite reduced absolute fit. Notably, the Recruitment likelihood contribution decreases in the ecosystem scenarios compared to the reference, which aligns with previous results showing constrained recruitment variability when ecological drivers are included. These variations may reflect differences in model assumptions or input data between scenarios, which could affect how well each model fits particular data sources. Table \@ref(tab:tablike) shows the log-likelihood component values for each scenario.

@@

Another step to measure the model performance in krill stock assessment was evaluated using the Root Mean Square Error (RMSE) across four scenarios of increasing ecological complexity (Figure \@ref(fig:rmseplot)). Scenario Model1.1, which excludes both environmental and predator variables, showed the lowest median RMSE and the narrowest interquartile range, suggesting higher consistency in model fits to observed data. The inclusion of ecosystem variables in Model1.2 (predator only), Model1.3 (environment only), and Model1.4 (both) resulted in increases in RMSE dispersion and median values, although the differences were relatively moderate. Among the ecosystem-informed scenarios, Model1.3 and Model1.4 had comparable RMSE distributions, slightly exceeding those of the predator-only model (Model1.2). The increased variability in RMSE under these scenarios suggests a reduction in overall fit quality when ecological complexity is introduced, likely reflecting increased model structural uncertainty or misalignment between ecological covariates and population dynamics.

```{r rmseplot, eval=TRUE, fig.cap="Root Mean Square Error (RMSE) distributions for four krill population model scenarios"}
knitr::include_graphics('Figs/diags2.png')
```

@@

Model outputs under different ecosystem scenarios revealed substantial variation in krill population indicators, including total biomass (Bio_all), summary biomass (Bio_smry), recruitment (Recruit_0), and spawning biomass (SpawnBio) (Figure \@ref(fig:popvar)). The reference model (s1.1), which excluded environmental and predator components, consistently produced higher median estimates and wider uncertainty intervals across all population indicators. Inclusion of predator components (s1.2) or environmental variables (s1.3) led to reductions in central tendency and variability for all metrics, with s1.3 (environment-only) showing the most constrained estimates, particularly for recruitment and spawning biomass. Scenario s1.4, which incorporated both environmental and predator components, resulted in intermediate biomass and recruitment estimates, with moderate variance compared to the other scenarios. Recruitment (Recruit_0) was especially sensitive to the inclusion of ecosystem components. The highest median recruitment was observed under s1.2 (predator-only), while the lowest was seen in s1.3 (environment-only), highlighting the contrasting influences of these ecological factors.

We compare the time series of different population variables for Antarctic krill under most significant models in this analysis; a reference model without environmental or predator data and an alternative model that incorporates both environmental and predator information. Total biomass estimates remain relatively stable across both scenarios until around 2010. From that point onward, both models show a marked increase in biomass, although the reference model predicts higher values than the ecosystem-informed model, particularly during the final assessment years (2018–2020). Recruitment at age 0 exhibits strong variability over time. This is coincidence with [REF]. While both models show similar patterns, the reference model tends to estimate higher recruitment peaks, especially in recent years. Finally, spawning biomass (SpawnBio) follows trends similar to total biomass. Both models show a gradual increase after 2010, but the reference model again yields higher values in recent years.

```{r compara,eval=TRUE, out.width="60%", fig.cap="Comparisons of krill population variables under scenarios of increasing ecosystem complexity. Metrics include total biomass (Bio_all), summary biomass (Bio_smry), recruitment (Recruit_0), and spawning biomass (SpawnBio)"}
knitr::include_graphics('Figs/alloutput_s1_4.png')
```

Biologically, ln(R0) represents the expected log-scale recruitment in the absence of fishing, providing a proxy for the reproductive potential or productivity of the population under pristine conditions. Figure \@ref(fig:compara2) displays posterior density distributions for the natural logarithm of virgin recruitment level (ln(R0)) across four model configurations. The narrow and well-separated peaks across models suggest that each model configuration yields distinctly different estimates of recruitment potential, likely reflecting differences in underlying assumptions such as natural mortality, selectivity, or the inclusion of predation effects. From a biological perspective, the higher ln(R0) values in `s1.3` and `s1.4` suggest that, under those model assumptions, the krill population could sustain higher levels of recruitment in unfished conditions, potentially reflecting stronger compensatory dynamics or reduced natural mortality (e.g., lower predation pressure). Conversely, the lower ln(R0) values in `s1.1` and `s1.2` imply a population with lower reproductive output, which might make it more vulnerable to overfishing or environmental variability. This highlights the sensitivity of the recruitment parameter to assumptions about ecological drivers in the stock-recruitment relationship.

@@

The stock–recruitment relationship was examined under two model scenarios: s1.1, a reference model excluding ecosystem components, and s1.4, which incorporates both environmental and predator data  (Figure \@ref(fig:proplot)). The plot illustrates the relationship between spawning stock biomass (SSB) and recruitment across years, overlaid with a fitted Beverton-Holt function derived from the model with ecosystem covariates. Scenario s1.1 (diamonds) displays a wider spread in recruitment estimates across the full range of SSB values, with several years (e.g., 2017, 2014) producing exceptionally high recruitment despite moderate to low SSB. In contrast, scenario s1.4 (crosses), which integrates ecosystem variables, generally shows lower recruitment estimates, with reduced variance and more clustered residuals at low SSB values. The fitted Beverton-Holt curve (in blue) from s1.4 captures the expected saturating recruitment response to increasing SSB. Notably, the inclusion of ecosystem variables appears to reduce extreme recruitment events and leads to a more stable, density-dependent recruitment pattern aligned with theoretical expectations. 
Estimating the productivity of Antarctic krill is critical for understanding the species capacity to replenish its population in response to varying levels of spawning biomass. Here, we defined the Productivity as the ratio of recruitment to spawning stock biomass, provides a standardized measure of reproductive success and population resilience under different ecological and fishing pressures. For each scenario \( i \) and year \( t \), we computed the productivity as the ratio between recruitment and spawning stock biomass (SSB):

$$
\text{Productivity}_{i,t} = \frac{\text{Recruitment}_{i,t}}{\text{SSB}_{i,t}}
$$
This plot illustrates the relationship between recruitment per unit of spawning stock biomass (Recruitment/SSB) and relative spawning stock biomass (SSB/SSBo) for four scenarios (s1.1 to s1.4)  (Figure \@ref(fig:proplot)). As expected under compensatory recruitment dynamics, all scenarios show a declining trend in productivity as SSB increases, indicating higher per-capita recruitment at low stock levels and reduced productivity as the population approaches its unfished biomass. The scenarios differ markedly in the magnitude of predicted productivity. Scenario s1.1 and s1.3 show higher productivity levels throughout the SSB range when compared to s1.2 and, most notably, s1.4. The latter scenario presents the lowest productivity values, indicating either reduced recruitment compensation or differences in the stock-recruitment parameters. These contrasting trends highlight how scenario-specific assumptions or structural choices influence estimates of productivity. These patterns reflect a more precautionary and ecologically realistic recruitment dynamic, where environmental variability limits the ability of the stock to maintain high productivity under depleted conditions. Overall, the results emphasize the influence of ecosystem variables on shaping recruitment dynamics and demonstrate that incorporating environmental drivers into the assessment model leads to more conservative productivity estimates, particularly at low spawning biomass levels.

```{r proplot, eval=TRUE, fig.cap="Left panel: Stock–recruitment relationships for Antarctic krill under four assessment scenarios. Predicted recruitment as a function of spawning stock biomass (SSB), with fitted Beverton-Holt curves and annual labels for selected years. Right panel: Recruitment per unit of SSB plotted against relative SSB (SSB/SSBo), illustrating differences in per-capita productivity across models ( s1.1 (no ecosystem variables), s1.2 (with predator effects), s1.3 (with environmental variables), and s1.4 (with both predator and environmental effects))"}
knitr::include_graphics('Figs/produc_com.png')
```

@@

```{r acfplot, eval=TRUE, fig.cap="Autocorrelation function (ACF) plots of model residuals for four krill assessment scenarios Blue dashed lines indicate 95% confidence intervals"}
knitr::include_graphics('Figs/ACF2.png')
```

A *t-test*, assuming normality and homoscedasticity, revealed a statistically significant difference in spawning biomass estimates between models `s1.1` and `s1.4` (*t = 4.2682, df = 72, p < 0.001*), with a 95% confidence interval for the mean difference ranging from *1,387,011 to 3,818,074*. Mean spawning biomass estimates were *4,600,304 t* for `s1.1` and *1,997,762 t* for `s1.4`. A non-parametric *Wilcoxon rank sum test* further confirmed this difference (*W = 1256, p < 0.001*), reinforcing the robustness of the result despite minor warnings due to ties in the dataset. These findings demonstrate that incorporating predator and environmental covariates into the population model (scenario `s1.4`) leads to significantly lower estimates of spawning biomass. This highlights the critical role of ecosystem components in influencing recruitment and population structure, and their importance in comprehensive stock assessment frameworks for krill.

@@

# Discusion

* **Big summary / importance statement for the science**

  * Expón de manera destacada la importancia científica de tus hallazgos generales.

* **Scientific findings as extension of previous work**

  * Relaciona tus hallazgos con trabajos previos y explica cómo los extienden o complementan.

@@

  * Detalla las implicancias científicas específicas de los resultados obtenidos.

* **How this engineering will facilitate future research**

  * Explica cómo tu enfoque metodológico o técnico puede ayudar a futuras investigaciones.

@@

  * Incluye reflexiones sobre cómo evolucionará el campo en general a partir de tu trabajo.

@@

  * Resume la importancia de la parte técnica o de ingeniería de tu estudio.

* **How it facilitates scientific research**

  * Describe cómo tus métodos o resultados facilitan la investigación científica práctica.

* **Limitations of the platform shown with questions that would be unanswered**

  * Reconoce limitaciones del estudio y plantea preguntas que aún quedan por responder.

By integrating ecosystem drivers into the stock assessment process, this study aims to demonstrate how incorporating environmental and ecological factors enhances the accuracy of Antarctic krill population estimates and improves the ability to predict future stock trends under changing climate and ecological conditions. This perspective seeks to strengthen the scientific foundation for sustainable management recommendations, ensuring that krill harvesting strategies align with CCAMLR’s ecosystem-based management approach. Ultimately, the insights gained from this integrated modeling effort contribute to CCAMLR’s ongoing strategy to balance the sustainability of the krill fishery with the conservation of the broader Antarctic marine ecosystem, supporting both the species that depend on krill as a primary food source and the long-term resilience of the Southern Ocean.

Data consistency

@@

The use of integrated models for assessing krill populations in the Southern Ocean has posed significant challenges for CCAMLR, particularly in light of the inherent uncertainties and limitations associated with data-poor regions. One of the key challenges is the reliance on models like the General Yield Model (GRYM) [REF], which assumes stable environmental conditions—a premise that increasingly fails to hold true in the context of ongoing climate change [REF]. GRYM, while useful for certain data-poor applications, faces difficulties due to its heavy dependence on life history parameters, such as growth rates, harvest strategies, and natural mortality. Moreover, the assumption of stable environmental conditions in such models is problematic [REF], as climate variability significantly influences krill productivity and survival. As a result, predictions based on GRYM and similar models become less reliable, particularly in the face of changing environmental conditions or ecological considerations. This highlights the need for more dynamic, ecosystem-informed approaches to stock assessment that consider the evolving nature of environmental and ecological drivers, such as changes in sea ice extent, primary productivity, and predator-prey interactions.

The transition from traditional, model-based approaches like GRYM to more integrated, ecosystem-based models presents a significant opportunity to improve the scientific basis of krill stock assessments. However, this shift also requires addressing the trade-offs between model complexity and data availability [REF]. While integrated models offer a more holistic view of krill population dynamics by incorporating ecosystem variables, they also introduce new challenges related to the accuracy and reliability of model inputs. Thus, the development of integrated models requires continuous refinement to ensure that they remain relevant and robust in the face of environmental change. [REF]

Management strategies should incorporate ecosystem-based thresholds informed by environmental and predation dynamics, as these factors are critical in maintaining krill availability for predators, which is essential for overall ecosystem balance. Additionally, the ongoing warming in the Antarctic Peninsula highlights the urgent need to integrate climate-driven changes into habitat suitability models, ensuring that management approaches remain adaptive to shifting environmental conditions.

Although integrated models are not new to krill in the Southern Ocean, CCAMLR has for years applied methodologies that incorporate diverse data sources. External reviews, such as @Thomson2016, have endorsed these approaches as improvements over traditional models. Previous studies like @Kinzey2011, @Kinzey2015a, @Kinzey2019a, and @Wang2021 have advanced integrated frameworks, though challenges like model convergence remain.

@@

> The three main penguin colonies Adélie, Chinstrap, and Gentoo are central place foragers with diet compositions that are strongly linked to krill abundance and demographic structure, particularly during the breeding season when foraging is spatially and temporally constrained [REF Lukcas!, REF Vicky].

> . This spatial overlap reinforces the ecological relevance of penguin-based indicators in reflecting krill dynamics

@@

### Stock-Recruitment and Biomass Estimates

>>>>

Understanding the population dynamics of Antarctic krill (*Euphausia superba*) is critical for achieving sustainable and ecosystem management objectives in the Western Antarctic Peninsula (WAP). In this study, we implement an integrated length-to-age model that not only allows the incorporation of diverse data sources related to krill population dynamics, but also enables the evaluation of ecosystem influences—specifically environmental variability and predation pressure—on recruitment, biomass, and stock status. We explored four scenarios that accounted (or not) for ecosystem influences on krill population dynamics, yielding results that align with the expected behavior of a stock assessment framework tailored to this type of species. Performance analyses reveal systematic differences across those scenarios, highlighting increased bias in fishing mortality (F) and spawning stock biomass (SSB) in models that exclude ecosystem variables. Conversely, the inclusion of environmental and predator data results in lower estimates of recruitment, total biomass, and spawning biomass, offering a more precautionary—and arguably more realistic—representation of krill population dynamics. Despite ongoing challenges in incorporating ecosystem variables into integrated model like this, we argue that these factors should be embedded directly into the state equations that govern population dynamics, rather than addressed through pre and post analyses. Overlooking these drivers may result in less accurate conclusions, hence limiting the effectiveness of management recommendations. Integrated modeling approaches that draw on extensive biological, ecologicl, fishery, and environmental datasets provide a valuable foundation for developing management strategies aligned with CCAMLR’s objectives for conservation and sustainable use.

or

Understanding the population dynamics of Antarctic krill (Euphausia superba) is essential for achieving ecosystem-based management objectives in the Western Antarctic Peninsula (WAP), particularly under the mandate of CCAMLR. In this study, we implement an integrated length-to-age assessment model designed to assimilate multiple data sources related to krill biology, fishery operations, and ecological interactions. A key feature of our approach is the explicit inclusion of ecosystem drivers—namely, environmental variability and predation pressure—as intrinsic components of the population dynamics. We evaluate four model scenarios, with and without ecosystem variables, and assess their performance in estimating recruitment, fishing mortality (F), total biomass, and spawning stock biomass (SSB). The comparison reveals systematic biases in models that omit ecological information, resulting in overestimated recruitment and biomass levels. In contrast, scenarios incorporating predator and environmental data yield more precautionary and biologically realistic outcomes, suggesting greater alignment with observed ecosystem variability. Despite ongoing challenges related to the availability, resolution, and integration of ecological data, we argue that environmental and trophic drivers should be embedded directly into the state-space structure of assessment models rather than treated as exogenous factors. Failing to do so may obscure key population processes and compromise the reliability of management advice. Our results underscore the potential of ecosystem-informed, integrated modeling frameworks to support robust, adaptive management strategies that align with CCAMLR’s conservation objectives, while also highlighting the continued need for methodological development and interdisciplinary data collection efforts in the Southern Ocean.

@@

The residuals are visualized by year and length bin, allowing an assessment of model fit over time and across the size structure of the population (Figure \@ref(fig:pearson)). In scenario s1.1, substantial lack of fit is evident across multiple years and length classes, particularly in the late 1990s and early 2000s. Positive Pearson residuals indicate that the model tends to underestimate frequencies of certain length bins, especially among smaller and mid-sized individuals, suggesting poor representation of recruitment and growth dynamics in the absence of environmental and predator effects. s1.2  shows some improvement in model fit, with slightly more balanced residuals. However, there are still consistent deviations in the mid-size ranges across multiple years, indicating that predation alone does not fully explain observed variability in length composition. In s1.3, there is a reduction in residual magnitude across several years and size classes, implying that incorporating environmental covariates helps align the model more closely with observed size distributions. This is particularly apparent in the early 2000s, where the residuals are closer to zero across most bins. Finally, s1.4 shows the most consistent reduction in Pearson residuals across time and size structure. The residual patterns also indicate potentially concerning model misfits, particularly among adult individuals in several survey fleets operating in the Bransfield Strait, as well as among the largest size classes in the predator fleet, which likely represents penguin consumption data. The residuals exhibit consistent over- or under-estimation in specific length bins over multiple years, suggesting that the current model structure may not fully capture key processes affecting the abundance or selectivity of adult individuals. In the case of surveys in Bransfield, this could reflect spatial mismatches between predicted and observed size distributions or biases in survey selectivity for larger size classes. This spatial heterogeneity aligns with previous findings identifying this area as a core juvenile krill habitat [@Mardones2025; @Veytia2021, Vetia et al., 2019, REF, REF]. Similarly, the residuals associated with the predator fleet suggest that the model may inadequately represent size-selective predation or the temporal dynamics of predator consumption. These patterns warrant further investigation into the assumptions underlying length selectivity and mortality, particularly for the adult component of the population, as well as potential ecosystem-driven variability not currently integrated in the model.

@@

```{r pearson, eval=TRUE, fig.cap= "Pearson residuals of predicted versus observed length-frequency distributions of Antarctic krill across four modeling scenarios (s1.1 to s1.4), each incorporating increasing levels of ecosystem complexity. Residuals are shown by fleet, survey, and predator source, allowing visual assessment of model fit across time and sampling components (BS=Bransfield Strait, EI= Elephant Island, GS= Gerlache Strait, JOIN= Joinville Island, SSWI= South West)"}
knitr::include_graphics('Figs/Pearson2.png')
```

@@

The retrospective pattern for fishing mortality (F) showed a marked increase in bias in scenario s1.2 and s1.4, which included predator components, particularly in the 2017 (Figure \@ref(fig:rhoplot)). In this scenario, the combined rho value exceeded 3.5, indicating a strong retrospective pattern. Scenarios s1.2 (predator only) and s1.3 (environment only) also showed elevated rho values relative to s1.1 (baseline model without ecosystem variables), although the magnitude was lower than in s1.4. In contrast, the retrospective pattern for spawning stock biomass (SSB) was consistently negative across all scenarios and years. However, models that included environmental components—s1.3 and s1.4—tended to show larger negative biases in SSB, with scenarios s1.2 and s1.4 again exhibiting the most pronounced pattern. The combined rho values for SSB in s1.3 and s1.4 were close to –0.5 and –0.6, respectively, whereas s1.1 showed a comparatively milder retrospective trend.

@@

Across all scenarios, the total log-likelihood is primarily influenced by the Survey, Length composition, and Recruitment components, with minor contributions from parameter priors. The reference model (s1.1) displays the highest overall likelihood value, particularly due to a stronger fit to the Length composition and Survey data. However, this comes with an elevated penalty in the parameters priors categories, suggesting potential overfitting or parameter instability. In contrast, the ecosystem-informed scenarios—s1.2 (with predator data), s1.3 (with environmental data), and s1.4 (with both)—show slightly lower total likelihoods. These models present more balanced likelihood contributions across data components and generally lower penalties for parameter priors and deviations, indicating a more stable parameterization despite reduced absolute fit. Notably, the Recruitment likelihood contribution decreases in the ecosystem scenarios compared to the reference, which aligns with previous results showing constrained recruitment variability when ecological drivers are included. These variations may reflect differences in model assumptions or input data between scenarios, which could affect how well each model fits particular data sources. Table \@ref(tab:tablike) shows the log-likelihood component values for each scenario. It summarizes the contributions of different data sources—such as survey indices, length composition, recruitment, and parameter priors—to the total likelihood in each model configuration (s1.1 to s1.4).

@@

The Root Mean Square Error (RMSE) analysis across four scenarios of increasing ecological complexity revealed that Scenario s1.1 -which excludes both environmental and predator variables- showed the lowest median RMSE and the narrowest interquartile range, suggesting higher consistency in model fits to observed data. The inclusion of ecosystem variables in s1.2 (predator only), s1.3 (environment only), and s1.4 (both) resulted in increases in RMSE dispersion and median values, although the differences were relatively moderate. Among the ecosystem-informed scenarios, s1.3 and s1.4 had comparable RMSE distributions, slightly exceeding those of the predator-only model (s1.2) (Figure \@ref(fig:rmseplot)). The increased variability in RMSE under these scenarios suggests a reduction in overall fit quality when ecological complexity is introduced, likely reflecting increased model structural uncertainty or misalignment between ecological covariates and population dynamics.

```{r rmseplot, eval=TRUE, fig.cap="Root Mean Square Error (RMSE) distributions for four krill population model scenarios"}
knitr::include_graphics('Figs/unnamed-chunk-29-1.jpeg')
```

@@

Model outputs under different ecosystem scenarios revealed substantial variation in krill population indicators, including total biomass (Bio_all), summary biomass (Bio_smry), recruitment (Recruit_0), and spawning biomass (SpawnBio) (Figure \@ref(fig:compara)). The reference model (s1.1), which excluded environmental and predator components, consistently produced higher median estimates and wider uncertainty intervals across all population indicators. Inclusion of predator components (s1.2) or environmental variables (s1.3) led to reductions in central tendency and variability for all metrics, with s1.3 (environment-only) showing the most constrained estimates, particularly for recruitment and spawning biomass. Scenario s1.4, which incorporated both environmental and predator components, resulted in intermediate biomass and recruitment estimates, with moderate variance compared to the other scenarios. Recruitment was especially sensitive to the inclusion of ecosystem components. The highest median recruitment was observed under s1.2 (predator-only), while the lowest was seen in s1.3 (environment-only), highlighting the contrasting influences of these ecological factors.

```{r compara,eval=TRUE, fig.cap="Comparisons of krill population variables under scenarios of increasing ecosystem complexity. Metrics include total biomass (Bio_all), summary biomass (Bio_smry), recruitment (Recruit_0), and spawning biomass (SpawnBio)"}
knitr::include_graphics('Figs/unnamed-chunk-66-1.jpeg')
```

Also, we compare the time series of different population variables (Figure \@ref(fig:compara1)). Total biomass estimates remain relatively stable across both scenarios until around 2010. From that point onward, both models show a marked increase in biomass, although the reference model predicts higher values than the ecosystem-informed model, particularly during the final assessment years (2018–2020). Recruitment at age 0 exhibits strong variability over time in coincidence with [@Dornam and REF]. While both models show similar patterns, the reference model tends to estimate higher recruitment peaks, especially in recent years. Finally, spawning biomass (SpawnBio) follows trends similar to total biomass. Both models show a gradual increase after 2010, but the reference model again yields higher values in recent years. A *t-test*, assuming normality and homoscedasticity, revealed a statistically significant difference in spawning biomass estimates between models `s1.1` and `s1.4` (*t = 4.2682, df = 72, p < 0.001*), with a 95% confidence interval for the mean difference ranging from *1,387,011 to 3,818,074*. Mean spawning biomass estimates were *4,600,304 t* for `s1.1` and *1,997,762 t* for `s1.4`. A non-parametric *Wilcoxon rank sum test* further confirmed this difference (*W = 1256, p < 0.001*), reinforcing the robustness of the result despite minor warnings due to ties in the dataset. These findings demonstrate that incorporating predator and environmental covariates into the population model (scenario `s1.4`) leads to significantly lower estimates of spawning biomass.

```{r compara1,eval=TRUE, fig.cap="Time series of population variables of krill in WAP: (A) total biomass (Bio_all), (B) summary biomass (Bio_smry), (C) recruitment (Recruit_0), and (D) spawning biomass (SpawnBio). Axes labels should clarify units (e.g., biomass in metric tons, recruitment in millions). Projections assume current management/environmental conditions."}
knitr::include_graphics('Figs/alloutput_variable2.png')
```

Biologically, ln(R0) represents the expected log-scale recruitment in the absence of fishing, providing a proxy for the reproductive potential or productivity of the population under pristine conditions. Figure \@ref(fig:compara2) displays posterior density distributions for the natural logarithm of virgin recruitment level (ln(R0)) across four model configurations. The narrow and well-separated peaks across models suggest that each model configuration yields distinctly different estimates of recruitment potential, likely reflecting differences in underlying assumptions such as natural mortality, selectivity, or the inclusion of predation effects. From a biological perspective, the higher ln(R0) values in s1.3 and s1.4 suggest that, under those model assumptions, the krill population could sustain higher levels of recruitment in unfished conditions, potentially reflecting stronger compensatory dynamics or reduced natural mortality (e.g., lower predation pressure). This highlights the sensitivity of the recruitment parameter to assumptions about ecological drivers in the stock-recruitment relationship.

@@

We compare the stock–recruitment relationship and productivity under all model scenarios with focus in differences between scenarios with and without ecosystems consideratios (s1.1 and s1.4). The left panel in Figure \@ref(fig:proplot) illustrates the relationship between spawning stock biomass (SSB) and recruitment across years, overlaid with a fitted Beverton-Holt function derived from the model with ecosystem covariates. Scenario s1.1 (diamonds) displays a wider spread in recruitment estimates across the full range of SSB values, with several years (e.g., 2017, 2014) producing exceptionally high recruitment despite moderate to low SSB. In contrast, scenario s1.4 (crosses), which integrates ecosystem variables, generally shows lower recruitment estimates, with reduced variance and more clustered residuals at low SSB values. The fitted Beverton-Holt curve (in blue) from s1.4 captures the expected saturating recruitment response to increasing SSB. Notably, the inclusion of ecosystem variables appears to reduce extreme recruitment events and leads to a more stable, density-dependent recruitment pattern aligned with theoretical expectations. We defined the stock productivity as the ratio of recruitment to spawning stock biomass, provides a standardized measure of reproductive success and population resilience under different ecological and fishing pressures. The The right panel in Figure \@ref(fig:proplot) illustrates the relationship between recruitment per unit of spawning stock biomass (Recruitment/SSB) and relative spawning stock biomass (SSB/SSBo) for four scenarios (s1.1 to s1.4). As expected under compensatory recruitment dynamics, all scenarios show a declining trend in productivity as SSB increases, indicating higher per-capita recruitment at low stock levels and reduced productivity as the population approaches its unfished biomass. The scenarios differ markedly in the magnitude of predicted productivity. Scenario s1.1 and s1.3 show higher productivity levels throughout the SSB range when compared to s1.2 and s1.4. The latter scenario presents the lowest productivity values, indicating either reduced recruitment compensation or differences in the stock-recruitment parameters. These contrasting trends highlight how scenario-specific assumptions or structural choices influence estimates of productivity.

```{r proplot, eval=TRUE, fig.cap="Left panel: Stock–recruitment relationships for Antarctic krill under four assessment scenarios (s1.1 to s1.4). Left panel: Predicted recruitment as a function of spawning stock biomass (SSB), with fitted Beverton-Holt curves and annual labels for selected years. Right panel: Recruitment per unit of SSB plotted against relative SSB (SSB/SSBo)"}
knitr::include_graphics('Figs/produc_com.png')
```

@@

```{r acfplot, eval=TRUE, fig.cap="Autocorrelation function (ACF) plots of model residuals for four krill assessment scenarios Blue dashed lines indicate 95% confidence intervals"}
knitr::include_graphics('Figs/ACF_Plot.png')
```

@@

# Discussion

(small guide)

* **Big summary / importance of this kind of integrated model in Krill**

* **Scientific main findings as extension of previous work (comparisons)**

@@

@@

@@

* **Limitations of Integrated models shown with questions that would be unanswered**

* **future work or recommendations to improve this**

One critical issue concerns the dependence on direct biomass estimates, which are typically derived from expensive and logistically demanding scientific surveys—most notably acoustic campaigns. These surveys, while highly informative, are methodologically complex and costly to repeat with sufficient temporal resolution. Furthermore, differences in survey design, calibration, and analytical protocols between campaigns introduce variability and uncertainty into biomass estimates, complicating their interpretation and use in long-term management decisions. On the other hand, CCAMLR currently employs a management framework that uses an indirect model called General Yield Model (GRYM) [REF]. This model approach assumes stable environmental conditions—a premise that increasingly fails to hold true in the context of ongoing climate change [REF]. GRYM, while useful for certain data-poor applications, faces difficulties due to its heavy dependence on life history parameters, such as growth rates, harvest strategies, and natural mortality. Moreover, the assumption of stable environmental conditions in such models is problematic [REF], as climate variability significantly influences the productivity and survival. As a result, predictions based on GRYM and similar models become less reliable, particularly in the face of changing environmental conditions or ecological considerations. This highlights the need made a transition to a **more realistic** for a integrated model and ecosystem-informed approaches to stock assessment that consider the evolving nature of environmental and ecological drivers, such as changes in sea ice extent, primary productivity, and predator-prey interactions.

@@

The transition from traditional, model-based approaches like GRYM to more integrated, ecosystem-based models presents a significant opportunity to improve the scientific basis of krill stock assessments. However, this shift also requires addressing the trade-offs between model complexity and data availability [REF]. While integrated models offer a more holistic view of krill population dynamics by incorporating ecosystem variables, they also introduce new challenges related to the accuracy and reliability of model inputs. Thus, the development of integrated models requires continuous refinement to ensure that they remain relevant and robust in the face of change in various dimensions [REF].

By integrating ecosystem drivers into the stock assessment process, this study aims to demonstrate how incorporating environmental and ecological factors enhances the accuracy of Antarctic krill population estimates and improves the ability to predict future stock trends under changing climate and ecological conditions in a realistic way. This perspective seeks to strengthen the scientific foundation for sustainable management recommendations, ensuring that krill harvesting strategies align with CCAMLR’s ecosystem-based management approach. Management strategies should incorporate ecosystem-based thresholds informed by environmental and predation dynamics, as these factors are critical in maintaining krill availability for predators, which is essential for overall ecosystem balance. Additionally, the ongoing warming in the WAP highlights the urgent need to integrate climate-driven changes into habitat suitability models, ensuring that management approaches remain adaptive to shifting environmental conditions. Ultimately, the insights gained from this integrated modeling effort contribute to CCAMLR’s ongoing strategy to balance the sustainability of the krill fishery with the conservation of the broader Antarctic marine ecosystem, supporting both the species that depend on krill as a primary food source and the long-term resilience of the Southern Ocean.

Although integrated models are not new to krill in the Southern Ocean, CCAMLR has for years applied methodologies that incorporate diverse data sources for several years. External reviews, such as @Thomson2016, have endorsed these approaches as improvements over traditional models. Previous studies like @Kinzey2011, @Kinzey2015a, @Kinzey2019a, and @Wang2021 have advanced integrated frameworks, though challenges like model convergence remain.

@@

@@

(Talk about decrease in penguins colonies at 2020 an impact in modeling)
